\papertitle

### 2021-05-25 source_separation/paper/paper.tex
Edit sec 3.3

		\subsection{Testing}\label{subsec:testing}
		In order to compare the effectiveness of the separation methods, a full target orchestration and a ground truth orchestration are done for each target. The full target orchestration is the orchestration of the target without any separation performed. The ground truth orchestration takes the four sources that make up the target and orchestrates each one separately, then combines them. This ground truth represents the orchestration that could take place if the separation method was perfect and separated a target exactly into its constituent sources.

		The procedure we use for testing is as follows:
		\begin{enumerate}
			\item The target is created as a combination of four randomly chosen sources, which are offset to begin playing at different times.
			\item The full target, without any separation performed, is orchestrated using the entire orchestra. This is called the \textbf{full target orchestration}.
			\item Each separation method is performed on the target, each splitting the target into four sub-targets. 
			\item The full orchestra is randomly split into four equal sized subsets, each containing 7 to 8 instruments.
			\item For each method, the four sub-targets are separately orchestrated, each using a different subset of the orchestra, and then each orchestration is combined to play simultaneously. This creates the \textbf{separated orchestrations}.
			\item The \textbf{ground truth orchestration} is created by orchestrating the four sources, using the same orchestra subsets from step 4, and then combined to play simultaneously.
			\item The distances between target and orchestration are calculated for the full target orchestration, the separated orchestration, and the ground truth orchestration. 
		\end{enumerate}

@@

		As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure \ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. The full target orchestration places all onsets at the beginning of the orchestration, since it is unable to differentiate between different sources, it cannot place the different orchestrations at the appropriate offsets. However, the separated orchestrations are able to correctly place the onsets of the sub-target orchestrations so far as the method has correctly separated out the sources. In the ground truth orchestration, the sources are offset by the same amount as they are in the creation of the target, leading to the ground truth having each source orchestration beginning at the correct time. For this reason, despite only performing static orchestrations, the resulting separated and ground truth orchestrations are offset in time compared to the full target orchestration.

>>>>

		\subsection{Testing}\label{subsec:testing}
		In order to compare the effectiveness of the separation methods, a full target orchestration and a ground truth orchestration are done for each target. The \textbf{full target orchestration} is the orchestration of the target without any separation performed. The \textbf{ground truth orchestration} takes the four sources that make up the target and orchestrates each one separately, then combines the orchestrations. This ground truth represents the orchestration that could take place if the separation method was perfect and separated a target exactly into its constituent sources.

		The procedure we use for testing is as follows:
		\begin{enumerate}
			\item The target is created as a combination of four randomly chosen sources, which are offset to begin playing at different times.
			\item The full target, without any separation performed, is orchestrated using the entire orchestra. This is called the full target orchestration.
			\item Each separation method is performed on the target, each splitting the target into four sub-targets. 
			\item The full orchestra is randomly split into four equal sized subsets, each containing 7 to 8 instruments.
			\item For each method, the four sub-targets are separately orchestrated, each using a different subset of the orchestra, and then each orchestration is combined to play simultaneously. This creates the \textbf{separated orchestrations}.
			\item The ground truth orchestration is created by orchestrating the four sources, using the same orchestra subsets from step 4, and then combined to play simultaneously.
			\item The distances between target and orchestration are calculated for the full target orchestration, the separated orchestration, and the ground truth orchestration. 
		\end{enumerate}

@@

		As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure \ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. In the full target orchestration, all onsets occur at the beginning of the orchestration. Since there is no knowledge of different sources, Orchidea cannot place the different orchestrations at the appropriate offsets. For the separated orchestrations, the onsets of the sub-target orchestrations can be placed at the correct offset if the separation method has correctly separated out the sources. In the ground truth orchestration, the sources are manually offset, leading to the ground truth having each source orchestration beginning at the correct time. For this reason, despite only performing static orchestrations, the resulting separated and ground truth orchestrations are offset in time compared to the full target orchestration.
